### 2018-07-10 FrascatiPlot/Paper/NucleiB2.tex
adding a sentence for the X(3872) in the outlook of the current version

In a follow-up publication, we will extend the study presented here to predictions for the $A$=4 systems introduced in Tab.~\ref{tab:nucleusradii} and to more exotic QCD objects like the X(3827). These predictions will be of outmost importance for the currently prepared physics case for LHC Run 3 \& 4 and beyond. In addition, our study is deliberately based on many simplifying assumptions in order to allow for a completely analytical treatment of the problem highlighting. Future studies will be based on more realistic approximations requiring numerical calculations.

@@

\begin{align}
	A& = 2 \qquad \qquad \nu_{2} = {3 \over {4\rmsd^2}}  \\
	A& = 3 \qquad \qquad \nu_{3} = {1 \over {\rmsthree^2}} \\
	A& = 4 \qquad \qquad \nu_{4} =  {9 \over {8\rmsfour^2}}
\end{align}

>>>>

In a follow-up publication, we will extend the study presented here to predictions for the $A$=4 systems introduced in Tab.~\ref{tab:nucleusradii} and to more exotic QCD objects like the X(3827). If the X(3872) corresponds to a loosely bound molecule composed of $D^{*0}$ and $D^{0}$ mesons, the rms of its wave-function can be as large as $4.9^{+13.4}_{-1.4}$~fm which is very similar to that of the hyper-triton. Thus, its production via a possible coalescence mechanism in pp collisions would be subject to similar suppression as the hyper-triton. These predictions will be of outmost importance for the currently prepared physics case for LHC Run 3 \& 4 and beyond. In addition, our study is deliberately based on many simplifying assumptions in order to allow for a completely analytical treatment of the problem highlighting. Future studies will be based on more realistic approximations requiring numerical calculations.

@@

\begin{align}
	A& = 2 \qquad \qquad \nu_{2} = {3 \over {4\rmsd^2}}  \\
	A& = 3 \qquad \qquad \nu_{3} = {1 \over {\rmsthree^2}} \\
	A& = 4 \qquad \qquad \nu_{4} =  {9 \over {8\rmsfour^2}} \;\; .
\end{align}
